% ========================================================================
% ABSTRACT EN INGLÉS
% ========================================================================

\chapter*{Abstract}

\textbf{Keywords:} data analytics, machine learning, big data, artificial intelligence, data mining, data science

\vspace{1cm}

[Here you should write a 300-500 word abstract of your thesis in English. The abstract should include:]

\textbf{Context and Problem:} Briefly describe the context of your research and the specific problem you address in the field of data analytics.

\textbf{Objectives:} Clearly state the main objectives of your thesis, both general and specific objectives.

\textbf{Methodology:} Concisely explain the methodology used, including data analytics techniques, machine learning algorithms, data processing tools, etc.

\textbf{Main Results:} Present the most important findings of your research, including performance metrics, discovered insights, or achieved improvements.

\textbf{Contributions:} Highlight the original contributions of your work to the field of data analytics.

\textbf{Conclusions:} Summarize the main conclusions and potential impact of your work.

\textbf{Applications:} Mention possible practical applications of your results in industry or future research.

Example structure:

This thesis presents [description of problem/opportunity] in the context of [specific domain]. The main objective was [general objective], through [main methodology]. Techniques of [specific techniques] were applied to [data description]. Results demonstrate [main results], achieving [specific metrics]. Main contributions include [specific contributions]. These findings have important implications for [applications/impact]. The work opens new research opportunities in [future areas].

\newpage
